The automotive industry is one of the biggest in the world, which increases the importance of ensuring integrity and trust in the vehicle
market. In this research, we presented a new framework based on HL fabric BC to record and secure all events in the vehicle lifecycle to
ensure trust between sellers and buyers in the market. Based on the evaluation results, our framework could provide significant value to the
market.

The framework functionality was assessed using manual testing and HL Explorer. Results showed that all test scenarios were successfully
executed with the framework operating without any critical issues. This demonstrates that the integration between framework parts is
reliable. Additionally, scalability was tested using HL caliper with a variation of organizations. Results show a potential for scaling by
either adding a new server for each organization or adding new peers to an organization. However, the framework gained a significant spike
when additional peers were added. Furthermore, latency was measured using HL caliper, although it should be noted that it was not intended
for single-machine benchmarking. Despite that, the results provided valuable insight. Latency was relatively high, which is explained by the
deployment on a single machine, also, network bandwidth was a limitation that caused the high latency and affected the overall performance,
nevertheless, network bandwidth should be taken into consideration when deploying to a real network. Finally, several security measures were
implemented, including TLS encryption, rate controller, and the use of spring security and JWT to handle authorization and authentication.
Despite these measures providing adequate protection, continuous improvements are essential to maintaining network integrity.

In future research, we would use security keys such as yubikey to store user certificates and explore the impact of using other languages
such as Go language and Node JS and databases such as level DB. OpenSearch can also be used to store and query images, it has the ability to
handle tremendous amounts of data and perform complex queries which can enhance image retrieval. Furthermore, Machine Learning (ML) and
Artificial Intelligence (AI) could be implemented to fairly estimate vehicle prices based on information retrieved from the framework.